Relationships in the extremes and their influence on competition and coexistence

### 2022-03-04 paper/Paper.Rnw
adding to last paragraph

\underline{caveats and future directions}
%Ellner et al (2016) points out that coexistence is also mediated by other factors that competition: shared enemies, 
%mutualist, facilitation etc. (these are the exact factors Ellner lists), so future work could explore 
%the importance of ATA for coexistence mediated by these factors.
%Something about spatial mechanisms of coexistence? We considered only mechanisms that applied in a model with
%solely temporal variation, but there are also spatial mechanisms. Need to learn about those and think about
%how to say something about how future work may be able to explore the importance of ATA in that context?

%Also need to talk about how this stuff will apply to data.
we used simple/extreme ATA
simple model and simple lab system
future work needed to assess the extent of how much ATA are important for complex field systems
what systems might be good? suggest systems and their important E vars.

Our investigation is a simple one; 
the ATA present is a perfect correlation is exactly one half of the relationship, 
but varying degrees of ATA may produce a similar result as well.

We used the most extreme version of asymmetric noise, i.e., perfect correlation changing to very low correlation at exactly the half point of the distribution, and a simple lottery model.

@@

\underline{conclude **NOT NEEDED**: how ur work answers/informs the broad question from the intro and lay out 2-3 key priorities for next research on this question}
We provided another showcase of the importance of ATAs in ecology, 
building on previous studies.
ATAs clearly have implications for coexistence and competition;
though more research is needed in exploring more complex models 
including spatiotemporal and multispecies models.
Hope to see this tertiary decomposition of MCT be applied to empirical research.
More investigations should be done to explore implications of ATAs 
to other ecological theories.

>>>>

\underline{caveats and future directions}
%Realism - we usede simple/extreme ATA, simple model and simple lab system, futurw work needed to assess 
%how mcuh ATA are important in complex systems, field systems
%what systems? what env vars?
%Ellner et al (2016) points out that coexistence is also mediated by other factors that competition: shared enemies, 
%mutualist, facilitation etc. (these are the exact factors Ellner lists), so future work could explore 
%the importance of ATA for coexistence mediated by these factors.
%Something about spatial mechanisms of coexistence? We considered only mechanisms that applied in a model with
%solely temporal variation, but there are also spatial mechanisms. Need to learn about those and think about
%how to say something about how future work may be able to explore the importance of ATA in that context?

%Also need to talk about how this stuff will apply to data.
As an introductory investigation of ATAs within the framework of coexistence theory, 
we used simple and extreme examples, and future work should include more realism and complexity
(assess more complex relationships, systems, and models). 
In our theoretical exploration, we implemented a simple lottery model and assessed 
the influence of extremely asymmetric associated noise, i.e., the noise was perfectly correlated
in exactly one half of the distribution. However, more complex models such as structured demographic models
or integral projection models should be explored and though similar results may be
produced, varying deegres of ATA, less extremely shaped?/
more moderately asymmetric / more realistic? relationships should be implemented.
Moreover, because our empirical application makes use of a simple and controlled lab system, future 
should be done to assess the extent of how much ATA are important for complex systems and field systems.

@@

%\underline{conclude **NOT NEEDED**: how ur work answers/informs the broad question from the intro and lay out 2-3 key priorities for next research on this question}
%We provided another showcase of the importance of ATAs in ecology, 
%building on previous studies.
%ATAs clearly have implications for coexistence and competition;
%though more research is needed in exploring more complex models 
%including spatiotemporal and multispecies models.
%Hope to see this tertiary decomposition of MCT be applied to empirical research.
%More investigations should be done to explore implications of ATAs 
%to other ecological theories.
